% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.21 of 2022/01/12
%
\documentclass[runningheads]{llncs}
%
\usepackage[T1]{fontenc}
% T1 fonts will be used to generate the final print and online PDFs,
% so please use T1 fonts in your manuscript whenever possible.
% Other font encondings may result in incorrect characters.
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following two lines
% to display URLs in blue roman font according to Springer's eBook style:
%\usepackage{color}
%\renewcommand\UrlFont{\color{blue}\rmfamily}
%\urlstyle{rm}
%
\usepackage{amsmath,mathtools}
\usepackage{colortbl}
\usepackage{algorithm2e}
\usepackage{multirow}
\usepackage{pgf}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage{nicematrix}
\usetikzlibrary{arrows, automata, fit, calc, positioning}
\usepackage{soul}
\usepackage[makeroom]{cancel}
\newcommand{\mycomment}[1]{}
\usepackage{subcaption}
\usepackage{wrapfig}
\usepackage{makecell} %new line in one table cell
% \usepackage[english,russian]{babel}

\begin{document}
%
\title{GLL-based Context-Free Path Querying for Neo4j}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{
Vadim Abzalov\inst{1}%\orcidID{1111-2222-3333-4444} 
\and Vlada Pogozhelskaya\inst{2} %\orcidID{1111-2222-3333-4444} 
\and Vladimir Kutuev \inst{1} \orcidID{0000-0001-7749-4940}
\and Olga Bachishche \inst{3}
\orcidID{0009-0007-5247-4362}
\and Semyon Grigorev\inst{1} \orcidID{0000-0002-7966-0698}
}
%
\authorrunning{V. Abzalov et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{
    Saint Petersburg State University, St. Petersburg, Russia 
    \\
    \email{vadim.i.abzalov@gmail.com},
    \email{\{v.kutuev,s.v.grigoriev\}@spbu.ru}
    \and
    National Research University Higher School of Economics, St. Petersburg, Russia 
    \email{vvpogozhelskaia@edu.hse.ru}
    \and 
    ITMO University, St. Petersburg, Russia
    \email{bach@niuitmo.ru}
}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
We propose a GLL-based \textit{context-free path querying} algorithm that handles queries in Extended Backus-Naur Form (EBNF) using Recursive State Machines (RSM). Utilization of EBNF allows one to combine traditional regular expressions and mutually recursive patterns in constraints natively. The proposed algorithm solves both the \textit{reachability-only} and the \textit{all-paths} problems for the \textit{all-pairs} and the \textit{multiple sources} cases. The evaluation on real-world graphs demonstrates that the utilization of RSMs increases the performance of query evaluation. Being implemented as a stored procedure for Neo4j, our solution demonstrates better performance than a similar solution for RedisGraph. The performance of our solution on regular path queries is comparable to the performance of the native Neo4j solution, and in some cases, our solution requires significantly less memory.

\keywords{Graph database \and graph querying \and context-free path querying \and CFPQ \and reachability problem \and all-paths problem \and generalized LL \and GLL}
\end{abstract}
%
%
%

\input{sections/introduction}
\input{sections/preliminaries}
\input{sections/rsm}
\input{sections/gll}
\input{sections/dataset}
\input{sections/bnf_vs_ebnf}
\input{sections/cfpq_for_neo4j}
\input{sections/related_work}
\input{sections/conclusion}

%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystyle{splncs04}
\bibliography{gll}
%
\input{sections/review}
\end{document}
